The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-08 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

(ref:cap-Fig2) Shows the home(blue) and away (red) scoring distirbutions for 2020(bottom) and 2017-2019(top)"
```{r Fig2, echo=FALSE, fig.cap="(ref:cap-Fig2)", fig.align='center'}
ggplot(combined) + 
  geom_histogram(aes(x = PTS, y = ..density.., fill = Home.Away), bins = 10, binwidth = 5)+
  facet_grid(Year ~ Home.Away)
```

>>>>

(ref:cap-Fig2) Shows the home(blue) and away (red) scoring distirbutions for 2020(bottom) and 2017-2019(top)"
```{r Fig2, echo=FALSE, fig.cap="(ref:cap-Fig2)", fig.align='center'}
ggplot(combined) + 
  geom_histogram(aes(x = PTS, y = ..density.., fill = Home.Away), bins = 10, binwidth = 5)+
  facet_grid(Year ~ Home.Away)+
  theme(legend.position = "none")
```
